---
title: "**NH tag**"
---

The following page details the distribution of NH tags in your bam sample. These stats come from running bamstats, information for this tool can be found <a href="http://bamstats.sourceforge.net/">here</a>

The NH (number of hits) tag can be useful for determining the number of occurances of the mate.

NH is an optional tag, not all aligners will include it (and those that do will often omit it for reads with only a single hit).


```{r nh, echo=FALSE}

library(knitr)
library("RSQLite")
library("DBI")
library(stringr)
library("rmarkdown") # Make cool dynamic documents
library("knitr") # Run R Code Chunks
library("ggplot2") # For plotting
library("DT") # Interactove html tables
library(ggplot2)
library(reshape2)

setwd("./..")
mydb <- dbConnect(RSQLite::SQLite(), "csvdb")
db <- dbGetQuery(mydb, 'SELECT * FROM bam_stats_nh;')


db <- melt(db, id.vars="nh")


fancy_scientific <- function(l) {
  # turn in to character string in scientific notation
  l <- format(l, scientific = TRUE)
  # quote the part before the exponent to keep all the digits
  l <- gsub("^(.*)e", "'\\1'e", l)
  # turn the 'e+' into plotmath format
  l <- gsub("e", "%*%10^", l)
  # return this as an expression
  parse(text=l)
}

ggplot(db, aes(x=nh, y=value, fill=variable, colour=variable)) + geom_bar(stat="identity") +
  theme_bw() + labs(x = "nh  tag", y="Counts")+
  theme(axis.text.x = element_text(angle = 90, hjust = 1), panel.border = element_blank(), 
        panel.grid.minor = element_blank(),panel.background = element_blank(),
        axis.line = element_line(colour = "black"))+
  scale_fill_brewer(palette="Set1") +
  scale_x_discrete(name="nh tag", limits=c(db[,"nh"]))+
  scale_y_continuous(labels=fancy_scientific)



```


The following table shows the individual results for each sample


```{r nh_table, echo=FALSE}

setwd("./..")
mydb <- dbConnect(RSQLite::SQLite(), "csvdb")
  db <- dbGetQuery(mydb, 'SELECT * FROM bam_stats_nh;')
  
  
  
  db <- t(db)
  colnames(db) <- db["nh",]
  db <- db[-which(rownames(db) %in% "nh"),]
  
  DT::datatable(as.data.frame(db, class = 'cell-border stripe'))

```

